\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage{fontawesome}
    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

\usepackage[dvipsnames]{xcolor}
\newcommand\myshade{85}
\colorlet{mylinkcolor}{violet}
\colorlet{myurlcolor}{Aquamarine}
\colorlet{mycitecolor}{NavyBlue}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
     linkcolor=black,
     urlcolor   = black!\myshade!black,
}

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
    % END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}

\vspace*{-40pt}

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Rupesh Harode}}\\
	{\faLinkedin \href{https://www.linkedin.com/in/techytoes/}{: techytoes}}
	$\cdot$
	{\faGithub \href{https://github.com/techytoes}{ : techytoes}}
	$\cdot$
	\href{mailto:rupeshharode@gmail.com}{rupeshharode@gmail.com} $\cdot$ +919479768157 $\cdot$ Mumbai, IN \\
\end{center}
\vspace*{1mm}
%==== Education ====%
\header{Education}
\textbf{Shri G.S. Institute of Technology and Science}\hfill Indore, IN\\
Bachelor of Engineering in Electronics and Telecommunication, CGPA: 7.26/10 \hfill Grad: Jun 2019\\
% Courses: Data Structures, Operating Systems, Algorithms, Computer Networks\\
\vspace*{1mm}
%==== Experience ====%
\header{Work Experience}
\textbf{SDE  \hfill Lido Learning} \hfill Aug 2019 | present\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\small{\item Implemented major UI features for all dashboards and improved overall user experience}
	\small{\item \textbf{Leveraged Knowledge:} NodeJS, ReactJS, GraphQL, AWS}
\end{itemize}

\textbf{SDE Intern  \hfill Greedy Game} \hfill June 2019 | July 2019\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\small{\item Integrated Prometheus and Grafana to monitor data and manage alerts using Go-kit toolkit.}
	\small{\item \textbf{Leveraged Knowledge:} Golang, Go-kit, Prometheus, Grafana.}
\end{itemize}


\textbf{Student Developer  \hfill Google Summer of Code} \hfill Apr 2018 | Aug 2018\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\small{\item Improved the communication plugin by adding VRPN and QSerial protocols into the communication plugin.}
	\small{\item  Added tests and documentation for VRPN and QSerial protocols and enhancing the test coverage to 96\%.}
	\small{\item \textbf{Leveraged Knowledge:} C++, QtCreator, VRPN, QSerial, Cmake}
\end{itemize}

\textbf{SDE, Intern  \hfill Naxap} \hfill Aug 2017 | Oct 2017\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\small{\item Implemented web-crawlers for 15+ torrent websites to crawl information essential for the search engine.}
	\small{\item Extracted Data using XPath and CSS Selectors and integrated methods to bypass Cloudflare challenges.}
	\small{\item \textbf{Leveraged Knowledge:} Python, Scrapy, Design Patterns}
\end{itemize}

%==== Projects ====%
\header{Projects \hfill \sl \small{Portfolio: \href{http://techytoes.github.io}{techytoes.github.io}} \hfill \faGithub \sl \small{ \href{https://github.com/techytoes}{github.com/techytoes}}}

\textbf{Multiplayer Quiz \href{https://github.com/techytoes/Multiplayer-Quiz}{\faGithub}}
\vspace{-1mm}
\begin{itemize}
	\small{\item Django based Web-application mainly focusing on API and Schema which allows users to participate in a multiplayer quiz.}
	\small{\item Implemented functionality like registration, login, adding question, creating game and playing game with a leaderboard to view progress of all users.}
	\vspace{-1mm}
	\small{\item \textbf{Used:} Python, Django, TastyPie, REST API.}
	\vspace{-1mm}
\end{itemize}

\textbf{Hackathon 3.0 \href{https://github.com/techytoes/publicSanitation}{\faGithub}}
\vspace{-1mm}
\begin{itemize}
	\small{\item Django based Web Application which shows most cleaned toilet nearby built as part of Hackathon, developed on top of GoogleMaps API.}
	\small{\item A real-time feedback system built using AJAX and Jquery integrated with BackEnd.}
	\vspace{-1mm}
	\small{\item \textbf{Used:} Python, Django, REST API, JS, Ajax, JQuery, ChartJS, Google Maps API.}
	\vspace{-1mm}
\end{itemize}

\textbf{Sentiment Analyzer \href{https://github.com/techytoes/Sentiment-Analyzer}{\faGithub}}
\vspace{-1mm}
\begin{itemize}
	\small{\item Examine the sentiment in terms of polarity (positive or negative) with an accuracy of 96.18\%}
	\small{\item MLP to implement NN model and NLTK is used to lemmatize .txt file.}
	\vspace{-1mm}
	\small{\item \textbf{Used:}  Python, TensorFlow, NLTK, Numpy.}
	\vspace{-1mm}
\end{itemize}

\vspace*{1mm}

\header{Leadership Experience}
\textbf{Technical Lead  \hfill Codefoster} \hfill Aug 2016 | Feb 2019\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\small{\item Codefoster is the coding club of SGSITS Indore with main purpose of nurturing the culture inside college.}
	\small{\item Supervised all the club activities which involves organizing coding events, workshops and internal discussions.}
\end{itemize}

%==== Skills ====%
\header{Skills}
\begin{tabular}{ l l }
	\small{\textbf{Languages}}      & \small{Python, Javascript, C/C++}      \\
	\small{\textbf{Technologies/Frameworks}} 
	&
	 \small{Django, NodeJS, ReactJS, GraphQL, Git, AWS}
	 \\
	\small{\textbf{Open Source Contributions}}      & \small{Sofa-Framework, Rspamd, Coala}               \\
% 	\small{\textbf{Competitive Programming}}                     &
% 	\href{https://www.hackerrank.com/k_akshay9721}{\underline{HackerRank}},
%     \href{https://codeforces.com/profile/k_akshay}{\underline{Codeforces}},
%     \href{https://www.codechef.com/users/kakshay21}{\underline{CodeChef}}
%     \\
% 	\small{\textbf{MOOCs}}                     &
% 	 \small{\href{https://www.coursera.org/account/accomplishments/verify/RL9PQEPWV5ZX}{\underline{Algorithms,}}
% 	 \href{https://www.coursera.org/account/accomplishments/verify/US5UEA64ENC5}{\underline{Parallel Programming,}} \href{https://www.coursera.org/account/accomplishments/verify/KTWGVEMQM4YQ}{\underline{Machine Learning Foundation,}} \href{https://www.coursera.org/account/accomplishments/verify/RGEFPE9K4T7D}{\underline{Neural Networks,}}}
\end{tabular}
\end{document}