%-------------------------
% Resume in Latex
% Author : Rupesh Harode
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://firedranzer.github.io/}{\Large Rupesh Harode}} & Email : \href{mailto:rupeshharode@gmail.com}{rupeshharode@gmail.com}\\
  \href{http://firedranzer.github.io/}{http://www.firedranzer.github.io} & Mobile : +91-947-976-8157 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Shri GS Institute of Technology and Science}{Indore, India}
      {Bachelor of Engineering in Electronics and Telecommunication}{Aug. 2015 -- May. 2019}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Google Summer of Code 2018}{Indore, India}
      {Student Developer at Sofa-Framework: C++, Cmake, QtCreator, Git}{April 2018 - Present}
      \resumeItemListStart
        \resumeItem{VRPN Protocol}
          {Improved the communication plugin by adding VRPN and QSerial protocols into the communication plugin which earlier had only ZMQ and OSC protocols.}
        \resumeItem{Extended Plugins}
          {Extended Communication plugin to ensure transmission of all types of messages.}
        \resumeItem{Testing and Documentation}
          {Added tests and documentation for VRPN and QSerial protocols and enhancing the test coverage.}
      \resumeItemListEnd

    \resumeSubheading
      {Naxap}{Remote}
      {Backend Developer Intern: Python, Scrapy, CSS, Xpath, PyCharm, Selenium}{Sept 2017 - Oct 2017}
      \resumeItemListStart
        \resumeItem{Web-Crawler}
          {Implemented several crawlers for different torrent websites for search engine.}
        \resumeItem{Cloudflare Challenges}
          {Extracted Data using XPath and CSS Selectors and integrated methods to bypass Cloudflare challenges.}
      \resumeItemListEnd
      
      \resumeSubheading
      {GoFind.ai}{Remote}
      {Data Analyst Intern: Python, MS-Excel}{July 2017 - Sept 2017}
      \resumeItemListStart
        \resumeItem{Data Cleanup}
          {Cleaned and validated data which was used to train classifiers. The model used for classification was Inception-v3.}
      \resumeItemListEnd
      
      \resumeSubheading
      {Club CodeFoster}{SGSITS}
      {Technical Lead}{July 2016 - Present}
      \resumeItemListStart
        \resumeItem{Workshops}
          {Club organizes competitive contests and programming events regularly.}
      \resumeItemListEnd
      
      

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Hackathon 3.0}{\href{https://github.com/firedranzer/publicSanitation}{https://github.com/firedranzer/publicSanitation}}
      {Tastypie(Django), Python, ChartJS, GoogleMaps API, Bootstrap}{Feb 2018}
      \resumeItemListStart
        \resumeItem{Web-Application}
          {Django based Web Application which shows most cleaned toilet nearby built as part of Hackathon, developed on top of GoogleMaps API.}
         \resumeItem{Review-System}
         {A real time feedback system built using AJAX and Jquery integrated with Back‐End.}
         \resumeItem{Dashboard}
         {A admin panel which displays usage statistics in the form of graph using ChartJS.}
      \resumeItemListEnd
      
      \resumeSubheading
      {Sentiment Analyzer}{\href{https://github.com/firedranzer/Sentiment-Analyzer}{https://github.com/firedranzer/Sentiment-Analyzer}}{Python, TensorFlow, NLTK, Numpy}{Oct 2017}
      \resumeItemListStart
        \resumeItem{Analyzer}
          {Examine the sentiment in terms of polarity (positive or negative) with an accuracy of 96.18\%.}
         \resumeItem{Neural-Network Model}
         {Multi‐layer perceptron to implement neural network model and NLTK is used to lemmatize .txt file and create lexicon.}
      \resumeItemListEnd
      
      \resumeSubheading
      {Zealer: Mini‐YouTube}{\href{https://github.com/firedranzer/zealer-mini-youtube}{https://github.com/firedranzer/zealer-mini-youtube}}{ReactJS, Javascript, Youtube API, HTML/CSS}{June 2017}
      \resumeItemListStart
        \resumeItem{Web-Application}
          {Web Application made on ReactJS Framework using YouTube‐API. Developed minimal JavaScript ES6 and JSX code supports real‐time loading enhanced.}
      \resumeItemListEnd
      
      \resumeSubheading
      {Putext}{\href{https://github.com/firedranzer/Putext}{https://github.com/firedranzer/Putext}}{Django, Python, xHTML2PDF, HTML/CSS}{March 2017}
      \resumeItemListStart
        \resumeItem{Web-Application}
          {Simple text to PDF converter on Django framework using xhtml2pdf library utilizing the MVC architecture.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd  
      
%\section{MOOC's Certificates}
 % \resumeSubHeadingListStart
  %
   % \resumeSubItem{Deeplearning.ai}
    %  {Neural Networks; Convolutional Neural Networks; }
    %\resumeSubItem{Mac Setup}
     % {Book that gives step by step instructions on setting up developer environment on Mac OS.}
     
  %\resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{MOOC}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{\href{https://www.coursera.org/account/accomplishments/verify/YNYSZK4QWWBN}{Neural }}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
