%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% Hyperlinks
\usepackage{hyperref}

% Set applicant's personal data for header
\name{Rupesh Harode}
\address{SGSITS College\linebreak Indore - 452003\linebreak Madhya-Pradesh, India}
\contacts{(+91) 947-976-8157 \linebreak rupeshharode@gmail.com \linebreak github.com/firedranzer}

\begin{document}

	% Print the header
	\makeheader

	\begin{cvsection}{Education}
		\begin{cvsubsection}{Indore, Madhya Pradesh, India}{SGSITS Indore}{}
			\begin{itemize}
				\item Bachelor of Engineering (B.E.) -- Electronics and Telecommunication Engineering from SGSITS, Indore.     CGPA: 7.34/10 (Current) \hfill May 2019 (Expected)
				\item Higher Secondary Education -- R D Public School, Betul. 93.20\%. \hfill May 2014
				\item Secondary Education -- R D Public School, Betul. CGPA: 9.2/10.\hfill May 2012
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	% Print the content
	\begin{cvsection}{Scholastic Achievements}{}{}
	Among the \textbf{1264 student} that are selected worldwide for \textbf{Google Summer of Code 2018} program under organization Sofa-Framework.
			\begin{itemize}
				\item Top 2\% in CBSE 2014 among 1 million students.
				\item Top 91 percentile in Qualitative aptitude and 99 percentile in Quantitative Aptitude, in PSA by CBSE.
                \item Regular competitive programmer with 90+ percentile in C++,C and Python on Hackerearth with an overall rating of 1305.
			\end{itemize}
		
	\end{cvsection}
	\begin{cvsection}{Work Experience}
	    \begin{cvsubsection}{Google Summer of Code}{SOFA-Framework}{April 2018 -- Present}
			\begin{itemize}
				\item Integrated VRPN protocol into communication plugin to send and receive data inside SOFA-Framework.
	   			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Backend Developer Intern}{NAXAP}{August 2017 -- October 2017}
			\begin{itemize}
				\item Based on Python library “Scrapy”, this project implements several crawlers for different torrent and websites.
	   			\item Extracted Data using XPath and CSS Selectors and integrated methods to bypass CloudFlare challenges.
	   			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Data Analyst Intern}{GoFind.ai}{July 2017 -- August 2017}
			\begin{itemize}
				\item Regular tasks involved validating data for training classifiers.
				\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Technical Knowledge}{}{}\\     \begin{cvsubsection}{Projects}{}{}
			\begin{itemize}
			    
			    \item \textbf{Public Sanitation} -- Django based Web Application developed on top of GoogleMaps API - Real time feedback system built using AJAX and Jquery integrated with Back-End - Admin panel which displays usage statistics in the form of graph using ChartJS.
			    
				\item \textbf{Python-OCR} -- Processed image using OpenCV and Numpy and extracted text using tesseract engine OCR.
				
	    		\item \textbf{Sentiment Analyzer} -- Sentiment Analyzer using TensorFlow, NLTK and Numpy with an accuracy of 96.18\% - NLTK is used to lemmatize .txt file and create lexicon 
			    
			    \item \textbf{Zealer: Mini-YouTube} -- Developed minimal JavaScript ES6 and JSX code supports real-time loading enhanced - Implemented Youtube-API which fetches data from Youtube asynchronously.
			    
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Positions of Responsibility}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item \textbf{Technical Lead, Codefoster} -- Club organizes competitive contests and programming events like workshops and coding sessions regularly.
			    \item \textbf{Coordinator, E-Cell SGSITS} -- Member of Entrepreneurship Cell of college. Actively involved in Event-planning, Graphics-designing and sponsorship for events.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Skills and Technologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item \textbf{Programming} -- C++/C, Python, MATLAB, MYSQL, Javascript, BASH
				\item \textbf{Development} -- QtCreator, HTML/CSS (with Bootstrap), Django, ReactJS, Adobe Photoshop, Adobe Illustrator
			    \item \textbf{Software Skills} -- Git(VCS), Cmake, AWS, Eagle, Proteus, GNU Octave, Xilinx
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
\end{document}
